<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-05-12 figures_01312022.Rmd
Chris's before leaving

@@

data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")

@@

### fix compound names
data$analyte_name_original[data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
data$analyte_name_original[data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
data$analyte_name_original[data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
data$analyte_name_original[data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"

@@

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(

  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(

  data.set = data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "fk_extraction_document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

# write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
# write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
# 
# write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
# write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
```

@@

### read in PK output files
pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")

pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")

### read in processed raw data files
raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")

raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")

@@

@@

save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")

save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")

### save cp data
# save(cp_df, file = "figures_rdata/cp_df.Rdata")
```

@@

### load all of this wonderful data
load("figures_rdata/pk_output_1comp_12212021.Rdata")
load("figures_rdata/pk_output_2comp_12212021.Rdata")
load("figures_rdata/raw_1comp_12212021.Rdata")
load("figures_rdata/raw_2comp_12212021.Rdata")
load("figures_rdata/cp_df_12212021.Rdata")
load("figures_rdata/cvt_variability_df_12212021.Rdata")

load("figures_rdata/pk_output_1comp_03012022.Rdata")
load("figures_rdata/pk_output_2comp_03012022.Rdata")
load("figures_rdata/pk_output_flat_03012022.Rdata")
load("figures_rdata/raw_1comp_03012022.Rdata")
load("figures_rdata/raw_2comp_03012022.Rdata")
load("figures_rdata/raw_flat_03012022.Rdata")
load("figures_rdata/cp_df_03012022.Rdata")
load("figures_rdata/cvt_variability_df_03012022.Rdata")

load("figures_rdata/cp_df_03302022.Rdata")

@@

@@

pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
  filter(Compound == "tamoxifen") %>%
  filter(Data.Analyzed != "Joint Analysis")

raw_1comp_03012022 <- raw_1comp_03012022 %>%
  filter(Compound == "tamoxifen")

junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
                      data.set = as.data.table(raw_1comp_12212021),
                      model = "1compartment")

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_03012022),
                      data.set = as.data.table(raw_2comp_03012022),
                      model = "2compartment")

@@

```{r, make_cp_rdata, eval = FALSE}
################################
### histogram showing data spread of invivoPKfit cp values
################################

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data1 <- dplyr::select(raw_1comp_03012022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs"))

@@

### function that finds cp
find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
                                                                                      params = full_data_1[1,],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}

### have to split data frame into ones with unique parameter values because cp_1comp takes constants
split_df_1 <- split(full_data_1, list(full_data_1$Compound,
                                      full_data_1$Reference,
                                      full_data_1$CAS),
                    drop = TRUE)

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_03012022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
full_data_2 <- full_data_2 %>% filter(AIC != Inf)
split_df_2 <- split(full_data_2, list(full_data_2$Compound,
                                      full_data_2$Reference,
                                      full_data_2$CAS),
                    drop = TRUE)

### function that finds cp
find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
                                                                                      params = full_data_2[1,],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}
cp_df_2 <- lapply(split_df_2, find_cp_2)

@@

pk_data_flat <- pk_output_flat_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data_flat <- dplyr::select(raw_flat_03012022, -c("A"))

@@

full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
full_data_flat <- full_data_flat %>% filter(AIC != Inf)
split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
                                            full_data_flat$Reference,
                                            full_data_flat$CAS),
                       drop = TRUE)

### function that finds cp
find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
                                                                                              params = full_data_flat[1,],
                                                                                              dose = Dose,
                                                                                              iv.dose = iv))}
cp_df_flat <- lapply(split_df_flat, find_cp_flat)

@@

cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value

cp_df <- cp_df %>% group_by(Species.x, 
                            Compound,
                            CAS,
                            type) %>%
  mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))

cp_df_03302022 <- cp_df

save(cp_df_03302022, file = "figures_rdata/cp_df_03302022.Rdata")
```

@@

@@

# data <- cp_df_12212021
data <- cp_df_03012022

@@

p <- ggplot(data = data,
            mapping = aes(x = cp_norm)) +
  geom_histogram(bins = 30) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  # xlim(0, 1e42) +
  # ylim(0, 400) +
  # scale_y_log10()+
  theme(title = element_text(size = 16),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14)) +
  scale_x_log10(limits = c(0.01, 1000)) +
  theme_bw() +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  facet_wrap(. ~ type)

@@

@@

# data <- cp_df_12212021
data <- cp_df_03012022

@@

@@

data <- cp_df_03012022

@@

@@

data <- as.data.table(raw_1comp_03012022)

@@

data.list <- list()
for(this.compound in unique(data[, Compound])) {
  this.compound.data <- data[Compound == this.compound]

@@

### combine data.tables back into one large data.set
cvt_variability_df_03012022 <- do.call(rbind, data.list)

save(cvt_variability_df_03012022, file = "figures_rdata/cvt_variability_df_03012022.Rdata")
```

@@

@@

data <- cvt_variability_df_03012022
# data <- cvt_variability_df_12212021

@@

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df_03302022

cvt_data <- cvt_variability_df_03012022

@@

@@

@@

@@

full_data_1 <- split_full_data$`1compartment`

>>>>

### this block runs the model fits
# and does some pre-processing to clean up the data

@@

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")

### these compounds had no CAS in the cvtdb
# double check and they should not have been added
# so I removed them

data <- data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")

@@

### fix compound names
data$analyte_name_original[data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
data$analyte_name_original[data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
data$analyte_name_original[data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
data$analyte_name_original[data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
data$analyte_name_original[data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"

@@

### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### uncomment below to export to CSV files
# change the date!!

write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.05092022.csv", row.names = FALSE)

write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.05092022.csv", row.names = FALSE)

write.csv(PK.fit.table.flat[[1]], "inst/ext/PK.fit.table.flat.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.flat[[2]], "inst/ext/processed.flat.data.05092022.csv", row.names = FALSE)
```

@@

### this block reads the exported model fit csv files from run_invivoPKfit

### read in PK output files
# pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
# pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
# pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")

# pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
# pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
# pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")

pk_output_1comp_04282022 <- read.csv("inst/ext/PK.fit.table.1comp.04282022.csv")
pk_output_2comp_04282022<- read.csv("inst/ext/PK.fit.table.2comp.04282022.csv")
pk_output_flat_04282022 <- read.csv("inst/ext/PK.fit.table.flat.04282022.csv")

pk_output_2comp_05092022 <- read.csv("inst/ext/PK.fit.table.2comp.05092022.csv")
pk_output_flat_05092022 <- read.csv("inst/ext/PK.fit.table.flat.05092022.csv")
pk_output_1comp_05092022 <- read.csv("inst/ext/PK.fit.table.1comp.05092022.csv")

### read in processed raw data files
# raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
# raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
# raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")

# raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
# raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
# raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")

# raw_1comp_04142022 <- read.csv("inst/ext/processed.1comp.data.04142022.csv")
# raw_2comp_04142022 <- read.csv("inst/ext/processed.2comp.data.04142022.csv")
# raw_flat_04142022 <- read.csv("inst/ext/processed.flat.data.04142022.csv")

raw_1comp_04282022 <- read.csv("inst/ext/processed.1comp.data.04282022.csv")
raw_2comp_04282022 <- read.csv("inst/ext/processed.2comp.data.04282022.csv")
raw_flat_04282022 <- read.csv("inst/ext/processed.flat.data.04282022.csv")

raw_1comp_05092022 <- read.csv("inst/ext/processed.1comp.data.05092022.csv")
raw_2comp_05092022 <- read.csv("inst/ext/processed.2comp.data.05092022.csv")
raw_flat_05092022 <- read.csv("inst/ext/processed.flat.data.05092022.csv")

@@

### this block takes the csv files in read_data
# and saves them as Rdata files

@@

# save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
# save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
# save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
# save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
# save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
# save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")

# save(pk_output_1comp_04142022, file = "figures_rdata/pk_output_1comp_04142022.Rdata")
# save(pk_output_2comp_04142022, file = "figures_rdata/pk_output_2comp_04142022.Rdata")
# save(pk_output_flat_04142022, file = "figures_rdata/pk_output_flat_04142022.Rdata")
# save(raw_1comp_04142022, file = "figures_rdata/raw_1comp_04142022.Rdata")
# save(raw_2comp_04142022, file = "figures_rdata/raw_2comp_04142022.Rdata")
# save(raw_flat_04142022, file = "figures_rdata/raw_flat_04142022.Rdata")

save(pk_output_1comp_05092022, file = "figures_rdata/pk_output_1comp_05092022.Rdata")
save(pk_output_2comp_05092022, file = "figures_rdata/pk_output_2comp_05092022.Rdata")
save(pk_output_flat_05092022, file = "figures_rdata/pk_output_flat_05092022.Rdata")
save(raw_1comp_05092022, file = "figures_rdata/raw_1comp_05092022.Rdata")
save(raw_2comp_05092022, file = "figures_rdata/raw_2comp_05092022.Rdata")
save(raw_flat_05092022, file = "figures_rdata/raw_flat_05092022.Rdata")

save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
```

@@

### this block loads the Rdata files,
# as well as some other files written in below code blocks
# this saves time from having to run those below code blocks every time
# these additional files include 'cp_df' and 'cvt_variability'

### load all of this wonderful data
# load("figures_rdata/pk_output_1comp_12212021.Rdata")
# load("figures_rdata/pk_output_2comp_12212021.Rdata")
# load("figures_rdata/raw_1comp_12212021.Rdata")
# load("figures_rdata/raw_2comp_12212021.Rdata")
# load("figures_rdata/cp_df_12212021.Rdata")
# load("figures_rdata/cvt_variability_df_12212021.Rdata")

# load("figures_rdata/pk_output_1comp_03012022.Rdata")
# load("figures_rdata/pk_output_2comp_03012022.Rdata")
# load("figures_rdata/pk_output_flat_03012022.Rdata")
# load("figures_rdata/raw_1comp_03012022.Rdata")
# load("figures_rdata/raw_2comp_03012022.Rdata")
# load("figures_rdata/raw_flat_03012022.Rdata")
# load("figures_rdata/cp_df_03012022.Rdata")
# load("figures_rdata/cvt_variability_df_03012022.Rdata")

# load("figures_rdata/pk_output_1comp_04142022.Rdata")
# load("figures_rdata/pk_output_2comp_04142022.Rdata")
# load("figures_rdata/pk_output_flat_04142022.Rdata")
# load("figures_rdata/raw_1comp_04142022.Rdata")
# load("figures_rdata/raw_2comp_04142022.Rdata")
# load("figures_rdata/raw_flat_04142022.Rdata")
# load("figures_rdata/cp_df_04142022.Rdata")
# load("figures_rdata/cvt_variability_df_04142022.Rdata")
# 
# load("figures_rdata/cp_df_03302022.Rdata")

# load("figures_rdata/pk_output_1comp_04282022.Rdata")
# load("figures_rdata/pk_output_2comp_04282022.Rdata")
# load("figures_rdata/pk_output_flat_04282022.Rdata")
# load("figures_rdata/raw_1comp_04282022.Rdata")
# load("figures_rdata/raw_2comp_04282022.Rdata")
# load("figures_rdata/raw_flat_04282022.Rdata")
# load("figures_rdata/cp_df_04282022.Rdata")
# load("figures_rdata/cvt_variability_df_04282022.Rdata")
# 
# load("figures_rdata/cp_df_04282022.Rdata")

load("figures_rdata/pk_output_1comp_05092022.Rdata")
load("figures_rdata/pk_output_2comp_05092022.Rdata")
load("figures_rdata/pk_output_flat_05092022.Rdata")
load("figures_rdata/raw_1comp_05092022.Rdata")
load("figures_rdata/raw_2comp_05092022.Rdata")
load("figures_rdata/raw_flat_05092022.Rdata")
load("figures_rdata/cp_df_05092022.Rdata")
load("figures_rdata/cvt_variability_df_05092022.Rdata")

load("figures_rdata/cp_df_05092022.Rdata")

@@

### this block produces the pdf files of the model fits
# plotted on top of the original data

@@

# pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
#   filter(Compound == "tamoxifen") %>%
#   filter(Data.Analyzed != "Joint Analysis")

# raw_1comp_03012022 <- raw_1comp_03012022 %>%
#   filter(Compound == "tamoxifen")

junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_05092022),
                      data.set = as.data.table(raw_1comp_05092022),
                      model = "1compartment")

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_05092022),
                      data.set = as.data.table(raw_2comp_05092022),
                      model = "2compartment")

junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat_05092022),
                      data.set = as.data.table(raw_flat_05092022),
                      model = "flat")

@@

```{r, make_cp_rdata, eval = FALSE}

### this block creates a data.frame of predicted concentrations
# using the estimated parameters and the observed conc-time points

######################

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data1 <- dplyr::select(raw_1comp_05092022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs")) %>% 
  filter(Species != "hamster")

@@

### function that finds cp
find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
                                                                                      params = full_data_1[1, ],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}

### have to split data frame into ones with unique parameter values because cp_1comp takes constants
split_df_1 <- split(full_data_1, list(full_data_1$Compound,
                                      full_data_1$Reference,
                                      full_data_1$CAS,
                                      full_data_1$Species.x),
                    drop = TRUE)

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_05092022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
full_data_2 <- full_data_2 %>% filter(AIC != Inf)
split_df_2 <- split(full_data_2, list(full_data_2$Compound,
                                      full_data_2$Reference,
                                      full_data_2$CAS,
                                      full_data_2$Species.x),
                    drop = TRUE)

### function that finds cp
find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
                                                                                      params = full_data_2[1, ],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}
cp_df_2 <- lapply(split_df_2, find_cp_2)

@@

pk_data_flat <- pk_output_flat_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data_flat <- dplyr::select(raw_flat_05092022, -c("A")) %>% 
  filter(Species != "hamster")

@@

full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
full_data_flat <- full_data_flat %>% filter(AIC != Inf)
split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
                                            full_data_flat$Reference,
                                            full_data_flat$CAS,
                                            full_data_flat$Species.x),
                       drop = TRUE)

### function that finds cp
find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
                                                                                              params = full_data_flat[1, ],
                                                                                              dose = Dose,
                                                                                              iv.dose = iv))}
cp_df_flat <- lapply(split_df_flat, find_cp_flat)

@@

# cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
# 
# cp_df <- cp_df %>% group_by(Species.x, 
#                             Compound,
#                             CAS,
#                             type) %>%
#   mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))

cp_df_05092022 <- cp_df

### here is where you save the Rdata file
save(cp_df_05092022, file = "figures_rdata/cp_df_05092022.Rdata")
```

@@

### this block makes a histogram of the data output
# from make_cp_rdata
# there's a separate facet for each model type
# only data that were best fitted by that model
# are shown in that facet

@@

pk_data <- cp_df_05092022

# cvt_data <- cvt_variability_df_04282022

@@

row.names(pk_data) <- c()
full_data <- pk_data

# cvt_data <- dplyr::select(cvt_data, -c("kelim",
#                                        "Vdist",
#                                        "Fgutabs",
#                                        "kgutabs"))
# 
# ### split pk_data by model so you can properly join with raw data
# model_split <- split(pk_data, pk_data$model)
# 
# cvt_data$Reference <- as.character(cvt_data$Reference)
# 
# cvt_data$type <- "1-Compartment"
# full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
# 
# cvt_data$type <- "2-Compartment"
# full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
# 
# cvt_data$type <- "Flat"
# full_data_flat <- left_join(cvt_data, model_split$`flat`)
# 
# ### put data back together
# full_data <- rbind(full_data_1, full_data_2, full_data_flat)
# 
# full_data <- full_data %>%
#   filter(cp != 0)

### only take necessary columns to keep things clean
full_data <- full_data %>%
  distinct(Compound, Reference, Species.x, model, AIC, cp_norm)

### this pivots the data so we have AICs and cp_norms
# for each model row-wise
full_data <- full_data %>%
  group_by(Species.x, Compound, Reference, model) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = model,
              values_from = c(AIC, cp_norm)) %>%
  dplyr::select(-row)

full_data <- as.data.table(full_data)

### make model column equal a specific model based on AIC values
full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment &
                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
                                                    AIC_2compartment < AIC_1compartment &
                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
                                                    AIC_flat < AIC_1compartment &
                                                      AIC_flat < AIC_2compartment ~ "Null",

                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
                                                      is.na(AIC_flat) ~ "1-Compartment",
                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) &
                                                      is.na(AIC_flat) ~ "2-Compartment",
                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) &
                                                      is.na(AIC_2compartment) ~ "Null",

                                                    is.na(AIC_1compartment) &
                                                      AIC_flat < AIC_2compartment ~ "Null",
                                                    is.na(AIC_1compartment) &
                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
                                                    is.na(AIC_2compartment) &
                                                      AIC_flat < AIC_1compartment ~ "Null",
                                                    is.na(AIC_2compartment) &
                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
                                                    is.na(AIC_flat) &
                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
                                                    is.na(AIC_flat) &
                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))

### make cp_norm equal to the cp_norm that corresponds to the best fitting model
full_data <- full_data %>%
  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
                             model == "2-Compartment" ~ cp_norm_2compartment,
                             model == "Null" ~ cp_norm_flat))

full_data[, model := paste("Model:", model)]

### this creates a new column that says how many unique sets of Compound, Reference,
# and Species correspond to each model
full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
                                                             "Reference",
                                                             "Species.x"), 
          by = "model"]

full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]

### make plot, facet by model and chem_ref_spec_count
p <- ggplot(data = full_data,
            mapping = aes(x = cp_norm)) +
  geom_histogram(binwidth = 0.325) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  # xlim(0, 1e42) +
  # ylim(0, 400) +
  # scale_y_log10()+
  theme(title = element_text(size = 16),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14)) +
  # scale_x_log10() +
  scale_x_log10(limits = c(1e-3, 1e3), labels = scientific) +
  scale_y_continuous(labels = scientific) +
  theme_bw() +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  facet_wrap(. ~ model + chem_ref_spec_count)

@@

### I think this is little outdated but whatever I'm gonna keep it here
# Think is was just plotting Cpred - Cobs

@@

# data <- cp_df_12212021
# data <- cp_df_03012022
data <- cp_df_04282022

@@

### I think this is little outdated but whatever I'm gonna keep it here

@@

data <- cp_df_04282022

@@

### this block creates a data.frame that shows the 
# spread of CvT data via across replicate timepoints 
# for a single experiment
# if the data isn't within 2-fold of itself
# is it reasonable to say that a model should fit within 2-fold?

@@

### all the raw data for each model SHOULD be the same
# so only need to use one
data <- as.data.table(raw_1comp_05092022)

@@

### this for loop applies the function 
# at data subsets of compound, data, dose, route, media
data.list <- list()
for(this.compound in unique(data[, Compound])) {
  this.compound.data <- data[Compound == this.compound]

@@

### combine data.tables back into one large data.set
cvt_variability_df_05092022 <- do.call(rbind, data.list)

### SAVE the data
save(cvt_variability_df_05092022, file = "figures_rdata/cvt_variability_df_05092022.Rdata")
```

@@

### this block makes the histogram
# of cvt variability using the data.frame
# made from make_cvt_variability_rdata

@@

data <- cvt_variability_df_05092022
# data <- cvt_variability_df_12212021

@@

### this block makes a density plot with cvt variabity
# and normalized predicted concentrations
# it's basically a combination of the other two histograms
# expect here we limit cp observations those that have replicate timepoint
# data, so it matches the cvt variability data, thus making it 
# comparable

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df_05092022

cvt_data <- cvt_variability_df_05092022

@@

### i hate row names
row.names(pk_data) <- c()

### making these null so I don't have to deal
# with duplicate .x and .y's
# only need the ones from pk_data
cvt_data <- dplyr::select(cvt_data, -c("kelim", 
                                       "Vdist", 
                                       "Fgutabs", 
                                       "kgutabs"))

@@

### References were of different classes for some reason
# so had to change
cvt_data$Reference <- as.character(cvt_data$Reference)

@@

### not sure why there were 0s,
# but they were screwing things up
full_data <- full_data %>%
  filter(cp != 0)

@@

full_data_1 <- split_full_data$`Model: 1-Compartment`
